Measuring and optimizing machine learning interpretability

### 2019-03-19 2019-03-21-dagstat-imlm/dagstat-molnar.Rmd
finishes slides

## We propose

TODO: Replace text with image: Black box in the middle, three properties attached to it

@@

$\Rightarrow$ Makes claims of interpretability more explicit ("Model A uses less features than B and has less interactions)

@@

TODO: Show result graphics

>>>>

## We propose measures of model complexity

@@

$\Rightarrow$ Makes claims of interpretability more explicit ("Model A uses less features than B and has less interactions")

@@

```{r, out.width='70%'}
knitr::include_graphics("../images/multi-obj-selection.png")
```
